Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-15 paper/evaluation.tex
Edited until result section

We evaluate guided proofreading on multiple different real-world connectomics datasets of different species. All datasets were acquired using either via serial section electron microscopy (ssEM) or serial section transmission electron microscopy (ssTEM). We perform experiments for error correction based on a selection oracle, automatic selection with threshold, and the forced choice setting. The latter is designed as a between-subjects user study with novice and expert participants.

@@

\textbf{L. Cylinder.} We use the left part of the 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels). The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse and was acquired using ssEM. The resolution of our dataset is $3\times3\, \text{nm}^2$ per pixel, and the section thickness is $30\, \text{nm}$. The image data and a manually-labeled expert segmentation is publicly available as ground truth for the entire dataset\footnote{The Kasthuri 3-cylinder mouse cortex volume is available at  https://software.rc.fas.harvard.edu/lichtman/vast/.}.
\\~\\
\textbf{AC4 subvolume.} This dataset is part of a publicly available dataset of mouse cortex that was published for the ISBI 2013 challenge "SNEMI3D: 3D Segmentation of neurites in EM images". The resolution of this dataset is $6\times6\times30~\text{nm}^3\text{/voxel}$ and it was acquired using ssEM. Haehn~\etal found the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes~\cite{haehn_dojo_2014}. This subvolume was used for Haehn~\etal~experiment on interactive proofreading tools for connectomics. We use the data, labeled ground truth and findings of their study which are published online\footnote{The AC4 subvolume and results of the interactive proofreading experiment are available at http://rhoana.org/dojo/.}. 
\\~\\
\textbf{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI) six ssTEM datasets (each $1250\times1250\times125$ voxels) were made publicly available\footnote{The MICCAI CREMI challenge data is available at http://www.cremi.org.}. Since only three include manually labeled ground truth, we use these three volumes for our experiments. The volumes are part of adult fruit fly (Drosophila melanogaster) brain. The resolution of all three datasets is $4\times4\times40~\text{nm}^3\text{/voxel}$. 
\\~\\
\textbf{Automatic segmentation pipeline.}
We use a state-of-the-art method to create a dense automatic segmentation of the data. Membrane probabilities are generated using a convolutional neural network based on the U-net architecture~\cite{RonnebergerFB15}. The probabilities are used to seed watershed and generate an oversegmentation using superpixels. Agglomeration is then performed by the GALA active learning classifier~\cite{nunez2014graph}.

@@

To train our split error classifier, we use the L. Cylinder dataset. We use the first 250 sections of the data for training and validation. For n-fold cross validation, we select one quarter of this data and re-select after each epoch. We minimize cross-entropy loss and update using stochastic gradient descent with Nesterov momentum \cite{nesterov}.
To generate training data, we identify correct regions and split errors in the automatic segmentation by intersection with ground truth regions. This is required since extracellular space is not labeled in the ground truth but in our dense automatic segmentation. 
From these regions, we sample 112,760 correct and 112,760 split error patches with 4-channels as described above. The patches are normalized and to further augment our training data, we rotate patches within each mini-batch by $k*90$ degrees with randomly chosen $k$. The training parameters such as filter size, number of filters, learning rate, and momentum are the result of intuition and experience, studying recent machine learning research, and a brute force parameter search within a limited range (see supplementary material). 
The first row of table~\ref{tab:parameters} lists the final parameters. Our CNN configuration results in approximately 170,000 learnable parameters. We assume that training has converged if the validation loss does not decrease for 50 epochs. We test the CNN by generating a balanced set of 8,780 correct and 8,780 error patches using unseen data of the left cylinder dataset and report testing results in the second row of table~\ref{tab:parameters}.

\begin{table}[h]
%\resizebox{\textwidth}{!}{%
\small
\begin{tabular}{l|l}
\begin{tabular}{l}
\textbf{Guided Proofreading}\\~\\
\textbf{Parameters} \\ 
Filter size: 3x3 \\ No. Filters 1: 64 \\ No. Filters 2-4: 48 \\ Dense units: 512 \\ Learning rate: 0.03-0.00001\\ Momentum: 0.9-0.999\\Mini-Batchsize: 128\\~\\
 \end{tabular}
&
\begin{tabular}{l}
\textbf{Focused Proofreading}\\~\\
\textbf{Parameters} \\ 
Iterations: 3 \\
Learning strategy: 2\\
Mito agglomeration: Off\\
Threshold: 0.0\\
~\\
~\\
~\\
~\\
 \end{tabular}
 \\
 \hline 
 \\
 \begin{tabular}{l}
\textbf{Results} \\ cost [m]: 383 \\ Val. loss: 0.0845 \\ Val. acc.: 0.969 \\ Test. acc.: 0.94 \\ Prec./Recall: 0.94/0.94 \\ F1 Score: 0.94
 \end{tabular}
&
\begin{tabular}{l}
\textbf{Results} \\ cost [m]: 217 \\ ~ \\ ~ \\ Test. acc.: 0.99 \\ Prec./Recall: ?/? \\ F1 Score: ?
 \end{tabular}
\end{tabular} 
\vspace{1mm}
\caption{Training parameters, cost and results of our guided proofreading classifier versus focused proofreading by Plaza \cite{focused_proofreading}. Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 graphics card).}%While the training of our classifier is more expensive, testing accuracy is superior. }
\label{tab:parameters}
\end{table}

@@

\textbf{Interactive proofreading.} A comparison of interactive proofreading tools by Haehn~\etal~ concludes that novices perform best when using Dojo~\cite{haehn_dojo_2014}. We use the publicly available findings of their user study as a baseline comparison. More specifically, we use the data of the Dojo user with the reported best performance.
\\~\\
\textbf{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}. Focused proofreading performs graph analysis on output from NeuroProof \cite{neuroproof2013}. For training, we therefore replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities. We obtained the best possible parameters for NeuroProof by consulting the developers and report them in table \ref{tab:parameters}. Rather than using Raveler as the frontend, we use our own interface (Figure \ref{fig:ui}). This way, the comparison is based on the classifier rather than on user interface.

@@

\textbf{Selection oracle evaluation.} We use the selection oracle as described in section~\ref{sec:errorcorrection} for the decision whether to accept or reject a correction. The purpose of this experiment is to investigate how many corrections are required to reach the best possible outcome. This is a direct comparison of the guided proofreading and focused proofreading classifiers but can only be performed if ground truth data is available. We perform this experiment on all datasets listed above.
\\~\\
\textbf{Automatic method evaluation.} For this experiment we accept all suggested corrections if the rankings are above a configured threshold $p_t=.95$ (Sec.~\ref{sec:errorcorrection}. We observed this value as stable in previous experiments with the guided proofreading classifiers (see supplementary material). We compare against the focused proofreading classifier and perform this experiment on all reported datasets.
\\~\\
\textbf{Forced choice user experiment.} We conduct a quantitative user study to evaluate the forced choice setting as described in section~\ref{sec:errorcorrection}. In particular, we evaluate how participants perform while correcting an automatic segmentation using the guided proofreading and focused proofreading tools. We designed a single factor between-subject experiment with the factor \textit{proofreading classifier} and asked participants to proofread the AC4 subvolume in a fixed time frame of 30 minutes. To enable comparison against the interactive proofreading study by~Haehn~\etal~, we use the exact same study conditions such as dataset and time limit. The experiment was performed on the same machine with standard, off-the-shelf hardware. All participants received monetary compensation for their time.
\begin{itemize}
\item \textbf{Novice Performance.} First we wanted to study how completely inexperienced users perform. We recruited participants with no experience in electron microscopy data or proofreading of such through flyers, mailing lists, and personal interaction. Based on sample size calculation theory, we estimated the study sample size as ten users per proofreading tool including four potential dropouts \cite{samplesize1, samplesize2}. Nevertheless, all twenty participants completed the study ($N=20$, 10 female; 19-65 years old, $M$=30). Each study session started off with the participants signing the consent form and with a five minute standardized explanation of the task. The participants then were asked to do a 3 minute proofreading task on separate but representative data using focused proofreading. The participants were allowed to ask questions during this time. The classifier did not matter in this case since the user interface was the same. The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment. After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation \cite{NASATLX}.
\item \textbf{Expert Performance.} We recruited 4 domain experts to evaluate performance of guided proofreading and focused proofreading. We obtained study consent and randomly assigned 2 experts to proofread using each classifier. The experts also did the 3 minute test run on different data prior to proofreading for 30 minutes. After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire as well.
\end{itemize}

>>>>

We evaluate guided proofreading extensively on multiple different real-world connectomics datasets of different species. All datasets were acquired using either via serial section electron microscopy (ssEM) or serial section transmission electron microscopy (ssTEM). We perform experiments for error correction based on a selection oracle, automatic selection with threshold, and the forced choice setting. The latter is designed as a between-subjects user study with novice and expert participants.

@@

\textbf{L. Cylinder.} We use the left part of the 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels). The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse and was acquired using ssEM. The resolution of our dataset is $3\times3\, \text{nm}^2$ per pixel, and the section thickness is $30\, \text{nm}$. The image data and a manually-labeled expert segmentation is publicly available as ground truth for the entire dataset\footnote{https://software.rc.fas.harvard.edu/lichtman/vast/}.
\\~\\
\textbf{AC4 subvolume.} This dataset is part of a publicly available dataset of mouse cortex that was published for the ISBI 2013 challenge "SNEMI3D: 3D Segmentation of neurites in EM images". The resolution of this dataset is $6\times6\times30~\text{nm}^3\text{/voxel}$ and it was acquired using ssEM. Haehn~\etal~\cite{haehn_dojo_2014} found the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes and used it for their experiments on interactive proofreading tools for connectomics. We use their publicly available data, labeled ground truth, and study findings~\footnote{http://rhoana.org/dojo/}.
\\~\\
\textbf{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI), six ssTEM datasets (each $1250\times1250\times125$ voxels) were made publicly available~\footnote{http://www.cremi.org}. Since only three include manually labeled ground truth, we use these three volumes for our experiments. The volumes are part of adult fruit fly (Drosophila melanogaster) brain. The resolution of all three datasets is $4\times4\times40~\text{nm}^3\text{/voxel}$.
\\~\\
\textbf{Automatic segmentation pipeline.}
We use a state-of-the-art method to create a dense automatic segmentation of the data. Membrane probabilities are generated using a convolutional neural network based on the U-net architecture~\cite{RonnebergerFB15}. The probabilities are used to seed watershed and generate an oversegmentation using superpixels. Agglomeration is then performed by the GALA active learning classifier~\cite{nunez2014graph}.

@@

To train our split error classifier, we use the L. Cylinder dataset. We use the first 250 sections of the data for training and validation. For n-fold cross validation, we select one quarter of this data and re-select after each epoch. We minimize cross-entropy loss and update using stochastic gradient descent with Nesterov momentum~\cite{nesterov}.
To generate training data, we identify correct regions and split errors in the automatic segmentation by intersection with ground truth regions. This is required since extracellular space is not labeled in the ground truth but in our dense automatic segmentation.
From these regions, we sample 112,760 correct and 112,760 split error patches with 4-channels as described above. The patches are normalized. To further augment our training data, we rotate patches within each mini-batch by $k*90$ degrees with randomly chosen $k$. The training parameters such as filter size, number of filters, learning rate, and momentum are the result of intuition and experience, studying recent machine learning research, and a brute force parameter search within a limited range (see supplementary material).
The first row of table~\ref{tab:parameters} lists the final parameters. Our CNN configuration results in approximately 170,000 learnable parameters. We assume that training has converged if the validation loss does not decrease for 50 epochs. We test the CNN by generating a balanced set of 8,780 correct and 8,780 error patches using unseen data of the left cylinder dataset and report testing results in the second row of table~\ref{tab:parameters}.

\begin{table}[h]
%\resizebox{\textwidth}{!}{%
\small
\begin{tabular}{l|l}
\begin{tabular}{l}
\textbf{Guided Proofreading}\\~\\
\textbf{Parameters} \\
Filter size: 3x3 \\ No. Filters 1: 64 \\ No. Filters 2-4: 48 \\ Dense units: 512 \\ Learning rate: 0.03-0.00001\\ Momentum: 0.9-0.999\\Mini-Batchsize: 128\\~\\
 \end{tabular}
&
\begin{tabular}{l}
\textbf{Focused Proofreading}\\~\\
\textbf{Parameters} \\
Iterations: 3 \\
Learning strategy: 2\\
Mito agglomeration: Off\\
Threshold: 0.0\\
~\\
~\\
~\\
~\\
 \end{tabular}
 \\
 \hline
 \\
 \begin{tabular}{l}
\textbf{Results} \\ cost [m]: 383 \\ Val. loss: 0.0845 \\ Val. acc.: 0.969 \\ Test. acc.: 0.94 \\ Prec./Recall: 0.94/0.94 \\ F1 Score: 0.94
 \end{tabular}
&
\begin{tabular}{l}
\textbf{Results} \\ cost [m]: 217 \\ ~ \\ ~ \\ Test. acc.: 0.99 \\ Prec./Recall: \HP{add}?/? \\ F1 Score: \HP{add}?
 \end{tabular}
\end{tabular}
\vspace{1mm}
\caption{Training parameters, cost, and results of our guided proofreading classifier versus focused proofreading by Plaza~\cite{focused_proofreading}. Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 GPU).\HP{Maybe split this into two tables?}}%While the training of our classifier is more expensive, testing accuracy is superior. }
\label{tab:parameters}
\end{table}

@@

\textbf{Interactive proofreading.} A comparison of interactive proofreading tools by Haehn~\etal~ concludes that novices perform best when using Dojo~\cite{haehn_dojo_2014}. We use the publicly available findings of their user study as a baseline comparison. More specifically, we use the data of the Dojo user with the reported best performance as a baseline.
\\~\\
\textbf{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}. Focused proofreading performs graph analysis on output from NeuroProof~\cite{neuroproof2013}. For training, we therefore replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities. We obtained the best possible parameters for NeuroProof by consulting the developers and report them in table~\ref{tab:parameters}. Rather than using Raveler as the frontend, we use our own interface (Fig.~\ref{fig:ui}). This way, the comparison is based on the classifier rather than on the user interface.

@@

\textbf{Selection oracle evaluation.} We use the selection oracle as described in Sec.~\ref{sec:errorcorrection} for the decision whether to accept or reject a correction. The purpose of this experiment is to investigate how many corrections are required to reach the best possible outcome. This is a direct comparison of the guided proofreading and focused proofreading classifiers but can only be performed if ground truth data is available. We perform this experiment on all datasets listed above.
\\~\\
\textbf{Automatic method evaluation.} For this experiment we accept all suggested corrections if the rankings are above a configured threshold $p_t=.95$ (Sec.~\ref{sec:errorcorrection}. We observed this value as stable in previous experiments with the guided proofreading classifiers (see supplementary material). We compare against the focused proofreading classifier and perform this experiment on all reported datasets.
\\~\\
\textbf{Forced choice user experiments.} We conducted a quantitative user study to evaluate the forced choice setting as described in Sec.~\ref{sec:errorcorrection}. In particular, we evaluate how participants perform while correcting an automatic segmentation using the guided proofreading and focused proofreading tools. We designed a single factor between-subject experiment with the factor \textit{proofreading classifier} and asked participants to proofread the AC4 subvolume in a fixed time frame of 30 minutes. To enable comparison against the interactive proofreading study by~Haehn~\etal~\cite{haehn_dojo_2014}, we use the exact same study conditions, dataset, and time limit. The experiment was performed on a machine with standard, off-the-shelf hardware. All participants received monetary compensation for their time.

\textbf{Novice Study Design.} We recruited participants with no experience in electron microscopy data or proofreading through flyers, mailing lists, and personal interaction. Based on sample size calculation theory, we estimated the study sample size as ten users per proofreading tool including four potential dropouts~\cite{samplesize1,samplesize2}. Nevertheless, all twenty participants completed the study ($N=20$, 10 female; 19-65 years old, $M$=30). Each study session started off with the participants signing the consent form and with a five minute standardized explanation of the task. The participants then were asked to do a 3 minute proofreading task on separate but representative data using focused proofreading. The participants were allowed to ask questions during this time. The classifier did not matter in this case since the user interface was the same. The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment. After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.

\textbf{Expert Study Design.} We recruited 4 domain experts to evaluate performance of guided proofreading and focused proofreading. We obtained study consent and randomly assigned 2 experts to proofread using each classifier. The experts also did the 3 minute test run on different data prior to proofreading for 30 minutes. After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire as well.

### 2016-11-15 paper/method.tex
Add more stuff.
Edited until result section

We build a split error classifier with output $p$ using a convolutional neural network (CNN) to check whether an edge within an existing automatic segmentation is valid ($p=0$) or not ($p=1$). Rather than analyzing every input pixel, the classifier operates only on segment boundaries which requires less pixel context and is faster. In contrast to Bogovic \etal~\cite{BogovicHJ13}, we work with 2D slices rather than 3D volumes. This enables proofreading prior or in parallel to a computationally expensive alignment of individual EM images.
\\~\\
\textbf{Convolutional Neural Network Architecture.} Split error detection of a given boundary is really a binary classification task since the boundary is either correct or erroneous. However, in reality the score $p$ is between 0 and 1. The classification complexity arises from hundreds of different cell types in connectomics data rather than from the classification decision itself. Intuitively, this yields a wider architecture with more filters rather than a deeper architecture with more layers. We explored different architectural configurations - including residual networks~\cite{resnet} - by performing a brute force parameter search and comparing precision and recall (see supplementary materials). Our final CNN configuration for split error detection is composed of four convolutional layers, each followed by max pooling as well as dropout regularization to prevent overfitting due to limited training data. Fig. \ref{fig:architecture} shows the CNN architecture for split error detection.
\\~\\
\textbf{Classifier Inputs.} To train the CNN for split error detection, we take boundary context information into consideration for the decision making process. For this, we use a $75\times75$ pixel patch at the center of an existing boundary. This covers approximately $80\%$ of all boundaries in real-world connectomics data with nanometer resolution. If the boundary length is not fully covered, we sample up to 10 non-overlapping patches along the boundary and combine the resulting score by weighted averaging based on boundary length coverage per patch. 
Similar to Bogovich~\etal~\cite{BogovicHJ13}, we use grayscale image data, corresponding boundary probabilities, and a single binary mask combining the two neighboring labels as features for our CNN. However, we observed that the boundary probability information generated from EM images is often misleading due to noise or artifacts in the data. This can result in merge errors within the automatic segmentation. To better direct our classifier to train on the true boundary, we extract the border between two segments. We then dilate this border by 5 pixels to consider slight edge ambiguities and use this binary mask as an additional feature to create a stacked 4-channel input patch. Fig. \ref{fig:cnn_inputs} shows examples of correct and erroneous feature patches and their corresponding automatic segmentation and ground truth.

@@

\subsection{Error Correction}

We use the proposed classifiers in combination to perform corrections of split and merge errors in automatic segmentations. For this, we first perform merge error detection for all existing segments in a dataset and store the inverted rankings $1-p$ as well as potential corrections. After that, we perform split error detection and store the ranking $p$ for all neighboring segments in the segmentation. We then sort the merge and split error rankings individually from highest to lowest. 
For error correction, we first loop through the potential merge error regions and then through the potential split error regions. During this process, each error is now subject to a yes/no decision which can be provided in different ways: 
\\~\\
\textbf{Selection oracle.} If ground truth data is available, the selection oracle \textit{knows} whether a possible correction improves an automatic segmentation. This is realized by simply comparing the outcome of a correction using a defined measure. The oracle only accepts corrections which improve the automatic segmentation - others get 
discarded. This equals perfect proofreading.
\\~\\
\textbf{Automatic selection with threshold.} The decision whether to accept or reject a potential correction is done by comparing rankings to a threshold $p_t$. If the inverted score $1-p$ of a merge error is higher than a threshold $1-p_t$, the correction is accepted. Similarly, a correction is accepted for a split error if the ranking $p$ is higher than $p_t$. Our experiments have shown that the threshold $p_t$ is the same for merge and split errors which makes sense for a balanced classifier, trained on equal numbers of correct and error patches.
\\~\\
\textbf{Forced choice setting.} A user is presented with the choices of either accepting or rejecting a correction. This way, all potential split errors are seen. Inspecting all merge errors is not possible for users due to the sheer amount of generated borders. We therefore only present merge errors which satisfy $1-p_t$. 
\\~\\
In all cases, a decision has to be made to advance to the next possible erroneous region. If a merge error correction was accepted, the newly found boundary is added to the segmentation data. This partially updates the merge error and split error ranking with respect to the new segment. If a split error correction was accepted, two segments are merged in the segmentation data and the disappearing segment is removed from all error rankings. We then perform merge error detection on the now larger segment and update the ranking. We also update the split error rankings to include all new neighbors and re-sort. The error with the next highest ranking is now subject to the yes/no decision.

@@

Guided proofreading is integrated into an existing workflow for large connectomics data. The system is web-based and is designed with a minimalistic user interface showing three components. We show the outline of the current labeling of a cell boundary and its proposed correction overlaying the EM image data. For the user, it is not possible to distinguish the current labeling and the proposed correction to avoid selection bias. We also show a solid overlay of the current and the proposed labeling. In addition, we show the image without overlays to provide an unoccluded view. User interaction is simple and involves one mouse click on either the current labeling or the correction. After interaction, the next potential error is shown. Figure \ref{fig:ui} shows the user interface.

\begin{figure}[h]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
\end{center}
  \vspace{-4mm}
   \caption{Segmentation correction with the guided proofreading user interface. An image without overlays is shown on the left. A split error (right) and its correction (center) are the possible choices for the user. Hovering highlights the current selection with a yellow border, and a mouse click confirms it by advancing to the next potential error.}
\label{fig:ui}
\end{figure}

>>>>

We build a split error classifier with output $p$ using a CNN to check whether an edge within an existing automatic segmentation is valid ($p=0$) or not ($p=1$). Rather than analyzing every input pixel, the classifier operates only on segment boundaries, which requires less pixel context and is faster. In contrast to Bogovic \etal~\cite{BogovicHJ13}, we work with 2D slices rather than 3D volumes. This enables proofreading prior or in parallel to a computationally expensive alignment of individual EM images.
\\~\\
\textbf{Convolutional Neural Network Architecture.} Split error detection of a given boundary is a binary classification task since the boundary is either correct or erroneous. However, in reality the score $p$ is between 0 and 1. The classification complexity arises from hundreds of different cell types in connectomics data rather than from the classification decision itself. Intuitively, this yields a wider architecture with more filters rather than a deeper architecture with more layers. We explored different architectural configurations--including residual networks~\cite{resnet}--by performing a brute force parameter search and comparing precision and recall (see supplementary materials). Our final CNN configuration for split error detection is composed of four convolutional layers, each followed by max pooling as well as dropout regularization to prevent overfitting due to limited training data. Fig.~\ref{fig:architecture} shows the CNN architecture for split error detection.
\\~\\
\textbf{Classifier Inputs.} To train the CNN for split error detection, we take boundary context information into consideration for the decision making process. For this, we use a $75\times75$ pixel patch at the center of an existing boundary. This covers approximately $80\%$ of all boundaries in real-world connectomics data with nanometer resolution. If the boundary length is not fully covered, we sample up to 10 non-overlapping patches along the boundary and combine the resulting score by weighted averaging based on boundary length coverage per patch.
%
Similar to Bogovich~\etal~\cite{BogovicHJ13}, we use grayscale image data,
corresponding boundary probabilities, and a single binary mask combining the two
neighboring labels as features for our CNN. However, we observed that the
boundary probability information generated from EM images is often misleading
due to noise or artifacts in the data. This can result in merge errors within
the automatic segmentation. To better direct our classifier to train on the true
boundary, we extract the border between two segments. We then dilate this border
by 5 pixels to consider slight edge ambiguities and use this binary mask as an
additional feature to create a stacked 4-channel input patch.
Fig.~\ref{fig:cnn_inputs} shows examples of correct and erroneous feature
patches and their corresponding automatic segmentation and ground truth.

@@

\subsection{Error Correction}
\label{sec:errorcorrection}

We use the proposed classifiers in combination to perform corrections of split and merge errors in automatic segmentations. For this, we first perform merge error detection for all existing segments in a dataset and store the inverted rankings $1-p$ as well as potential corrections. After that, we perform split error detection and store the ranking $p$ for all neighboring segments in the segmentation. We then sort the merge and split error rankings individually from highest to lowest.
For error correction, we first loop through the potential merge error regions and then through the potential split error regions. During this process, each error is now subject to a yes/no decision which can be provided in different ways:
\\~\\
\textbf{Selection oracle.} If ground truth data is available, the selection oracle \textit{knows} whether a possible correction improves an automatic segmentation. This is realized by simply comparing the outcome of a correction using a defined measure. The oracle only accepts corrections which improve the automatic segmentation---others get
discarded. This equals perfect proofreading.
\\~\\
\textbf{Automatic selection with threshold.} The decision whether to accept or reject a potential correction is done by comparing rankings to a threshold $p_t$. If the inverted score $1-p$ of a merge error is higher than a threshold $1-p_t$, the correction is accepted. Similarly, a correction is accepted for a split error if the ranking $p$ is higher than $p_t$. Our experiments have shown that the threshold $p_t$ is the same for merge and split errors for a balanced classifier that has been trained on equal numbers of correct and error patches.
\\~\\
\textbf{Forced choice setting.} A user is presented with the choices of either accepting or rejecting a correction. This way, all potential split errors are seen. Inspecting all merge errors is not possible for users due to the sheer amount of generated borders. We therefore only present merge errors that satisfy $1-p_t$.
\\~\\
In all cases, a decision has to be made to advance to the next possible erroneous region. If a merge error correction was accepted, the newly found boundary is added to the segmentation data. This partially updates the merge error and split error ranking with respect to the new segment. If a split error correction was accepted, two segments are merged in the segmentation data and the disappearing segment is removed from all error rankings. We then perform merge error detection on the now larger segment and update the ranking. We also update the split error rankings to include all new neighbors and re-sort. The error with the next highest ranking is now subject to the yes/no decision.

@@

Our guided proofreading is integrated into an existing workflow for large connectomics data. The system is web-based and is designed with a user-friendly user interface (Fig.\ref{fig:ui}) showing three components. We show the outline of the current labeling of a cell boundary and its proposed correction overlaying the EM image data. For the user, it is not possible to distinguish the current labeling and the proposed correction to avoid selection bias. We also show a solid overlay of the current and the proposed labeling. In addition, we show the image without overlays to provide an unoccluded view. User interaction is simple and involves one mouse click on either the current labeling or the correction. After interaction, the next potential error is shown.

\begin{figure}[h]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
\end{center}
  \vspace{-4mm}
   \caption{Our guided proofreading user interface for Segmentation correction. An image without overlays is shown on the left. A split error (right) and its correction (center) are the possible choices for the user. Hovering highlights the current selection with a yellow border, and a mouse click confirms it by advancing to the next potential error.}
\label{fig:ui}
\end{figure}
